A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-11 doc/large_strain.tex
say how memory bandwidth is measured

% likwid-mpirun -np 10 -nperdomain S:10 -g MEM_DP -m $EXC
{\color{red}
Finally, we analyze the node-level performance of the two approaches using the Roofline model.
Memory bandwidth (MBytes/s) and the number of floating point operations per second (MFLOP/s) are measured using the \texttt{MEM\_DP} group of the LIKWID \cite{likwid} tool, version 4.2.1.
The measurements are done on a single socket of RRZE cluster by pinning all 10 MPI processes to this socket, whose
memory bandwidth and peak performance are $B=50 \,\rm{GB/s}$ and $P=176\, \rm{GFLOP/s}$, respectively.
}

>>>>

% likwid-mpirun -np 10 -nperdomain S:10 -g MEM_DP -m $EXC
{\color{red}
Finally, we analyze the node-level performance of the two approaches using the Roofline model.
Memory bandwidth (MBytes/s) and the number of floating point operations per second (MFLOP/s) are measured using the \texttt{MEM\_DP} group of the LIKWID \cite{likwid} tool, version 4.2.1.
The measurements are done on a single socket of RRZE cluster by pinning all 10 MPI processes to this socket, whose
memory bandwidth\footnote{As measured with the \textit{load\_avx} benchmark of \textit{likwid-bench} \cite{likwid}.} and peak performance are $B=47.2 \,\rm{GB/s}$ and $P=176\, \rm{GFlop/s}$, respectively.
}
